\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-03-11 docs/paper/paper.tex
Introduction preface Fixed filenames

@@

Machine learning techniques are coming to the forefront of many fields. Especially deep learning [ref], surpassing human performance in a variety of fields, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology. However, this flexibility does not stop here because Artificial Neural Networks can compute any function at all (Universality theorem)[ref]. No matter what the function is, there is to be a ANN so that for every possible vector X, the value f(X) (or some close approximation) is output from the network [ref]. This fact propelled researchers to widen the applications of ANNs even further, including the study of nanophotonic structures [ref], optimization of photonic crystal nanocavities [ref], and more recently in a similar work to this paper, computing optical properties of a photonic crystal fiber [ref]. Perhaps one of the challenges that deep learning models face is that they benefit from large amounts of data to train, which is quite costly to acquire [ref]. One of the solutions to overcome this issue is to artificially expand the original real data set by the means of generative networks. Introduced by Goodfellow et al., Generative Adversarial Networks (GANs) [ref], proved to be very impressive in tasks such as synthetic data generation [ref], Synthetically Augment data for deep learning based image segmentation [ref]. GANs power comes from the fact that they discover insights and structures within distributions that allows them to make good approximations to the real data set. In this paper we focus on determining one of the propagation features of a multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model. Our aim to eventually surpass the simulations performed using Full-Vectorial Finite Element Method (FV-FEM) to design, optimise and evaluate the sensor performance. A time comparison between the performance of the ANN and classic simulation techniques has been made here [ref]. Furtheremore, a time comparaison is also made in this paper in section $4$.

@@

\hl{Short explanation of GAN/ANN}

>>>>

In this paper we propose the use of artificial neural networks (ANN) to compute the loss in photonic crystal fibers in a wide range of configurations. Additionally, in order to minimize the required amount of samples to train the ANN, we employed generative adversarial networks (GAN). As discussed in the experiments section, this setup significantly reduces the error in the prediction compared to the state-of-the-art methods used in the literature.

@@

Machine learning techniques are coming to the forefront of many fields [ref], surpassing the human performance in many tasks, namely automatic speech recognition, image recognition, natural language processing, drug discovery and toxicology. Additionally, ANN can approximate any function (Universality theorem)[ref]. This fact propelled researchers to widen the applications of ANN even further, including the study of nanophotonic structures [ref], optimization of photonic crystal nanocavities [ref], and more recently, computing optical properties of a photonic crystal fiber [ref].

One of the most difficult challenges that deep learning models face is that they benefit from large amounts of data to train, which may be costly to acquire [ref]. One of the solutions to overcome this issue is to artificially expand the original dataset by the means of generative networks. Introduced by Goodfellow et al., Generative Adversarial Networks (GAN) [ref], proved to be successful in tasks such as synthetic data generation [ref] and synthetically augment the data for deep learning based systems [ref].

\hl{Will be moved to methodology} 
hl{GAN power comes from the fact that they discover insights and structures within distributions that allows them to make good approximations to the real data set.} \hl{This is exactly how ANN works too.} In this paper we focus on determining one of the propagation features of a multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR), that is the confinement loss, by using an Artificial Neural Network model, and a special kind generative networks to expand our limited data set for the purpose of  improving the accuracy of our ANN model. Our aim to eventually surpass the simulations performed using Full-Vectorial Finite Element Method (FV-FEM) to design, optimise and evaluate the sensor performance. A time comparison between the performance of the ANN and classic simulation techniques has been made here [ref]. Furtheremore, a time comparaison is also made in this paper in section $4$.

@@
